---
title: "Credit risk EDA"
author: "Anupriya Kushwanshi"
date: "May 27, 2019"
output: html_document
---
Insights:
1 is good and 2 is bad.


.	70% customers are good and 30% are bad.  
.	50% of "good" customers do not have checking accounts and 45% defaulters have less than 0 Deutsche Mark in their checking accounts.  
.	51% "good" customers paid existing credits till now and nearly 30% have critical account or other credits existing (not at this bank). More than 56% defaulters paid existing credits till now.  
.	For good customers, most common purpose for taking the loan is radio/television whereas for defaulters it's car.  
.	More than 50% good customers and nearly 70% bad customers have less than 100 Deutsche Mark in their accounts.  
.	Employment is almost well distributed among the customers with 1-4 year of work experience having a better share. Very few(~7.6%) are unemployed.  
.	57% good customers and 49% bad customers single males.  
.	91% good and bad customers have no other debtors.  
.	31% good customers have properties in the form of real state and 33% in car. The proportion is almost same among the bad customers.  
.	84% of good customers and 75% of bad customers have no other installment plans. 
.	75% good customers and 62% bad customers own a house.  
.	64% good customers and 62% bad customers are skilled employees or officials.  
.	95% good customers and 99% bad customers are foreign employees.  



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

german_credit = read.table("http://archive.ics.uci.edu/ml/machine-learning-databases/statlog/german/german.data")
colnames(german_credit)=c("chk_acct","duration","credit_his","purpose","amount","saving_acct","present_emp","installment_rate","sex","other_debtor","present_resid","property","age","other_install","housing","n_credits","job","n_people","telephone","foreign","response")
head(german_credit)
```
```{r}
str(german_credit)
```

  
```{r}
library(tidyverse)
(nrow(filter(german_credit, chk_acct == 'A11' & response == 2))/nrow(filter(german_credit,response == 2 )))*100
(nrow(filter(german_credit, chk_acct == 'A14' & response == 1))/nrow(filter(german_credit,response == 1 )))*100

german_credit%>%
ggplot(aes(response, fill=chk_acct))+geom_bar()
```
Status of existing checking account  
A11 : ... < 0 DM  
A12 : 0 <= ... < 200 DM  
A13 : ... >= 200 DM / salary assignments for at least 1 year  
A14 : no checking account

  
```{r}
(nrow(filter(german_credit, credit_his == 'A32' & response == 2))/nrow(filter(german_credit,response == 2 )))*100
(nrow(filter(german_credit, credit_his == 'A32' & response == 1))/nrow(filter(german_credit,response == 1 )))*100

german_credit%>%
ggplot(aes(response, fill=credit_his))+geom_bar()
```

Credit history  
A30 : no credits taken/ all credits paid back duly  
A31 : all credits at this bank paid back duly  
A32 : existing credits paid back duly till now  
A33 : delay in paying off in the past  
A34 : critical account/ other credits existing (not at this bank)
```{r}
german_credit%>%
ggplot(aes(response, fill=purpose))+geom_bar()
```


Purpose 
A40 : car (new) 
A41 : car (used) 
A42 : furniture/equipment 
A43 : radio/television 
A44 : domestic appliances 
A45 : repairs 
A46 : education 
A47 : (vacation - does not exist?) 
A48 : retraining 
A49 : business 
A410 : others 

```{r}
german_credit%>%
ggplot(aes(response, fill=saving_acct))+geom_bar()
```
Savings account/bonds 
A61 : ... < 100 DM 
A62 : 100 <= ... < 500 DM 
A63 : 500 <= ... < 1000 DM 
A64 : .. >= 1000 DM 
A65 : unknown/ no savings account 

```{r}
(nrow(filter(german_credit, present_emp == 'A71' & response == 2))/nrow(filter(german_credit,response == 2 )))*100

german_credit%>%
ggplot(aes(response, fill=present_emp))+geom_bar()
```
Present employment since 
A71 : unemployed 
A72 : ... < 1 year 
A73 : 1 <= ... < 4 years 
A74 : 4 <= ... < 7 years 
A75 : .. >= 7 years 

```{r}
(nrow(filter(german_credit, sex == 'A93' & response == 2))/nrow(filter(german_credit,response == 2 )))*100
(nrow(filter(german_credit, sex == 'A93' & response == 1))/nrow(filter(german_credit,response == 1 )))*100

german_credit%>%
ggplot(aes(response, fill=sex))+geom_bar()
```
Personal status and sex 
A91 : male : divorced/separated 
A92 : female : divorced/separated/married 
A93 : male : single 
A94 : male : married/widowed 
A95 : female : single 
```{r}
(nrow(filter(german_credit, other_debtor == 'A101' & response == 2))/nrow(filter(german_credit,response == 2 )))*100
(nrow(filter(german_credit, other_debtor == 'A101' & response == 1))/nrow(filter(german_credit,response == 1 )))*100

german_credit%>%
ggplot(aes(response, fill=other_debtor))+geom_bar()
```
Other debtors / guarantors 
A101 : none 
A102 : co-applicant 
A103 : guarantor 
```{r}
(nrow(filter(german_credit, property == 'A121' & response == 1))/nrow(filter(german_credit,response == 1 )))*100
(nrow(filter(german_credit, property == 'A123' & response == 1))/nrow(filter(german_credit,response == 1 )))*100


german_credit%>%
ggplot(aes(response, fill=property))+geom_bar()
```
A121 : real estate 
A122 : if not A121 : building society savings agreement/ life insurance 
A123 : if not A121/A122 : car or other, not in attribute 6 
A124 : unknown / no property 
```{r}
german_credit%>%
ggplot(aes(response, fill=property))+geom_bar()
```
```{r}
(nrow(filter(german_credit, other_install == 'A143' & response == 2))/nrow(filter(german_credit,response == 2 )))*100
(nrow(filter(german_credit, other_install == 'A143' & response == 1))/nrow(filter(german_credit,response == 1 )))*100

german_credit%>%
ggplot(aes(response, fill=other_install))+geom_bar()
```
Other installment plans 
A141 : bank 
A142 : stores 
A143 : none 
```{r}
(nrow(filter(german_credit, housing == 'A152' & response == 2))/nrow(filter(german_credit,response == 2 )))*100
(nrow(filter(german_credit, housing == 'A152' & response == 1))/nrow(filter(german_credit,response == 1 )))*100

german_credit%>%
ggplot(aes(response, fill=housing))+geom_bar()
```
Housing 
A151 : rent 
A152 : own 
A153 : for free 


```{r}
(nrow(filter(german_credit, job == 'A173' & response == 2))/nrow(filter(german_credit,response == 2 )))*100
(nrow(filter(german_credit, job == 'A173' & response == 1))/nrow(filter(german_credit,response == 1 )))*100

german_credit%>%
ggplot(aes(response, fill=job))+geom_bar()
```
Job 
A171 : unemployed/ unskilled - non-resident 
A172 : unskilled - resident 
A173 : skilled employee / official 
A174 : management/ self-employed/ 
highly qualified employee/ officer 

```{r}
(nrow(filter(german_credit, foreign == 'A201' & response == 2))/nrow(filter(german_credit,response == 2 )))*100
(nrow(filter(german_credit, foreign == 'A201' & response == 1))/nrow(filter(german_credit,response == 1 )))*100


german_credit%>%
ggplot(aes(response, fill=foreign))+geom_bar()
```

foreign worker 
A201 : yes 
A202 : no 
```{r}
(nrow(filter(german_credit,  response == 2))/nrow(german_credit))*100
(nrow(filter(german_credit,  response == 1))/nrow(german_credit))*100

german_credit$response <- as.factor(german_credit$response)
german_credit%>%
ggplot(aes(age))+geom_bar(aes(fill=response))+facet_wrap(~response)

```

```{r}

german_credit%>%
ggplot(aes(amount))+geom_histogram(aes(fill=response))+facet_wrap(~response)

```